Draft Research pt3

### 2019-03-17 draftResearch_pt3.Rmd
Trying some draft results summary research

```{r}
positions_tiers %>%
  filter(round > 17) %>%
  ggplot(aes(x=position, y=z_sum, alpha = desc(round))) +
  geom_jitter(aes(text=Name), width = .3) -> pt_even

@@

>>>>

```{r}
positions_tiers %>%
  filter(round > 23) %>%
  ggplot(aes(x=position, y=z_sum, alpha = desc(round))) +
  geom_jitter(aes(text=Name), width = .3) -> pt_even

@@

drafted_players_190316 <- c(
  "Chris Sale",
  "Bryce Harper",
  "Joey Votto",
  "Carlos Carrasco",
  "Justin Turner",
  "Daniel Murphy",
  "Joey Gallo",
  "Josh Hader",
  "Aaron Hicks",
  "Carlos Santana",
  "Trevor Story",
  "Dellin Betances",
  "David Robertson",
  "Will Smith",
  "Andrew Miller",
  "Kyle Schwarber",
  "Josh Bell",
  "Soo Choo",
  "Brandon Belt",
  "Chad Green",
  "Wilmer Flores",
  "Keone Kela",
  "Ryan Pressly"
  )

drafted_team_190316 <- df_join_positions %>%
  filter(Name %in% drafted_players)

drafted_batters_190316 <- drafted_team_190316 %>%
  filter(type == "Batter") %>%
  mutate(OB = PA * OBP,
         SLG = OPS - OBP,
         AB = PA - H,
         TB = SLG * AB) %>%
  summarize(PA = sum(PA),
            H = sum(H),
            HR = sum(HR),
            R = sum(R),
            RBI = sum(RBI),
            BB = sum(BB),
            SO = sum(SO),
            SB = sum(SB),
            OBP = sum(OB) / PA,
            SLG = sum(TB) / sum(AB),
            OPS = OBP + SLG
            )

drafted_pitchers_190316 <- drafted_team_190316 %>% 
  filter(type == "Pitcher") %>%
  mutate(ER = IP/9 * ERA,
         runners = WHIP * IP) %>%
  summarize(IP = sum(IP),
            SV = sum(SV),
            HLD = sum(HLD),
            ERA = sum(ER) / (IP/9),
            WHIP = sum(runners) / IP)

drafted_team_stats_190316 <- drafted_batters_190316 %>%
  bind_cols(drafted_pitchers_190316)
